### 2017-07-07 motivation.tex
Edits.

\begin{figure}
\centering
\begin{ocaml}
let new_order d_id c_id item_reqs = atomically do
  dist <- SQL.select1 District (fun d -> d.d_id = d_id);
  let o_id = dist.d_next_o_id;
  SQL.update District (fun d -> {d with d_next_o_id =d_next_o_id + 1})
                      (fun d -> d.d_id = d_id );
  SQL.insert Order {o_id=o_id;  o_d_id=d_id; 
                    o_c_id=c_id; o_ol_cnt=S.size item_reqs; };
  foreach item_reqs @@ fun item_req -> do
    stk <- SQL.select1 Stock (fun s -> s.s_i_id = item_req.ol_i_id &&
                                       s.s_d_id = d_id);
    let s_qty' = if stk.s_qty >= item_req.ol_qty + 10 
                then stk.s_qty - item_req.ol_qty 
                else stk.s_qty - item_req.ol_qty + 91;
    SQL.update Stock (fun s -> {s with s_qty = s_qty'}) 
                     (fun s -> s.s_i_id = item_req.ol_i_id);
    SQL.insert Order_line {ol_o_id=o_id; ol_d_id=d_id; 
                           ol_i_id=item_req.ol_i_id; ol_qty=item_req.ol_qty}

>>>>

\begin{figure}
\centering
\begin{ocaml}
let new_order d_id c_id item_reqs = atomically do
  dist <- SQL.select1 District (fun d -> d.d_id = d_id);
  let o_id = dist.d_next_o_id;
  SQL.update(* UPDATE *) District 
            (* SET *)(fun d -> {d with d_next_o_id =d_next_o_id + 1})
            (* WHERE *)(fun d -> d.d_id = d_id );
  SQL.insert(* INSERT INTO *) Order (* VALUES *){o_id=o_id;  
            o_d_id=d_id; o_c_id=c_id; o_ol_cnt=S.size item_reqs; };
  foreach item_reqs @@ fun item_req -> do
    stk <- SQL.select1(* SELECT * FROM *) Stock 
              (* WHERE *)(fun s -> s.s_i_id = item_req.ol_i_id 
                                  && s.s_d_id = d_id)(* LIMIT 1 *); 
    let s_qty' = if stk.s_qty >= item_req.ol_qty + 10 
                then stk.s_qty - item_req.ol_qty 
                else stk.s_qty - item_req.ol_qty + 91;
    SQL.update Stock (fun s -> {s with s_qty = s_qty'}) 
                     (fun s -> s.s_i_id = item_req.ol_i_id);
    SQL.insert Order_line {ol_o_id=o_id; ol_d_id=d_id; 
                           ol_i_id=item_req.ol_i_id; ol_qty=item_req.ol_qty}
